---
title: "homework3"
author: "Zach Wang"
format: html
---

##Part 1
```{r}
library("tidyverse")
library("here")
library("flextable")
library("janitor")
```

##Part 2
#a.
I could calculate the mean sleep time for different calorie ranges to see if there's a pattern in how sleep duration changes with daily energy expenditure. This comparison is informative because higher calorie burn might reflect more physical activity, which could influence sleep quality or duration.

#b
```{r}
setwd("/Users/zach/Desktop/git/ENVS-193DS_homework-03/data")
mydata <- read_csv("my_data.csv") |> #adding the data
  clean_names()

# using scatter plot to visusalize the data
ggplot(mydata, aes(x = calories, #add data frame
                   y = sleeptime,
                   fill = calories)) +
  geom_jitter(width = 0.2, #add plots
              shape = 21,
              alpha = 0.5,
              color = "lightblue") + #change color of plots

  labs(
    title = "Average Sleep Duration by Calorie Burn ", #add labels
    subtitle = "Zach Wang",
    x = "Calorie Burned per day (cal)",
    y = "Sleep Duration (Hours)"
  ) +
  theme_minimal() +
  theme(legend.position = "none") #custom legends



```

#c
This scatter plot displays the relationship between my daily calories burned and sleep duration (in hours). Each point represents a day of recorded data, represent variation in sleep relative to physical activity. While no clear linear trend is evident, most of the observation are located at the left side of the graph, which means most days the calories burned are no more than 2900 cal. All the observation are less than 9 hours. And the observations at the left hand side show a wide range of spreading means huge variance of sleep time.








































