---
title: "homework3"
author: "Zach Wang"
format: html
---

##Problem 1
##Part 1
```{r}
library("tidyverse")
library("here")
library("flextable")
library("janitor")
```

##Part 2
#a.
I could calculate the mean sleep time for different calorie ranges to see if there's a pattern in how sleep duration changes with daily energy expenditure. This comparison is informative because higher calorie burn might reflect more physical activity, which could influence sleep quality or duration.

#b
```{r}
setwd("/Users/zach/Desktop/git/ENVS-193DS_homework-03/data")
mydata <- read_csv("my_data.csv") |> #adding the data
  clean_names()

# using scatter plot to visusalize the data
ggplot(mydata, aes(x = calories, #add data frame
                   y = sleeptime,
                   fill = calories)) +
  geom_jitter(width = 0.2, #add plots
              shape = 21,
              alpha = 0.5,
              color = "lightblue") + #change color of plots

  labs(
    title = "Average Sleep Duration by Calorie Burn ", #add labels
    subtitle = "Zach Wang",
    x = "Calorie Burned per day (cal)",
    y = "Sleep Duration (Hours)"
  ) +
  theme_minimal() +
  theme(legend.position = "none") #custom legends



```

#c
This scatter plot displays the relationship between my daily calories burned and sleep duration (in hours). Each point represents a day of recorded data, represent variation in sleep relative to physical activity. While no clear linear trend is evident, most of the observation are located at the left side of the graph, which means most days the calories burned are no more than 2900 cal. All the observation are less than 9 hours. And the observations at the left hand side show a wide range of spreading means huge variance of sleep time.

#d
```{r}

summary_table <- mydata |> #data frame
  group_by(calories) |> #adjust table
  summarise(mean_sleeptime = round(mean(sleeptime, na.rm = TRUE), 1)) |> #calculation
  rename( #rename labels
    "Calories (cal)" = calories,
    "Mean Sleep Time (Hours)" = mean_sleeptime
  )
flextable(summary_table) #showing tables
```

##Problem 2
#a.
I designed symbols for each different observation. The symbol looks like a triangle, the height of the triangle represent the sleep time. The width of the triangle represent the the calories I burned in the same day. On the top there is a bar, which means I did 5km running in that day. If there is no bar, then I did not do running that day. Now I can use the size and shape of triangle to fully communicate with others about my data.

#b.

insert
```{r}
! [ ](photon.jpg)

print(getwd())
```

#c.
insert

#d.
My photo is showing every individual observations I recorded. Stefanie Posavec and Grogia Lupi's Dear Data project inspired me to most via their icons. The form of my work is pencil drawing. At first, I was trying to present my data without the traditional axes since it looks boring and it takes time for people to gather the information for each observation. So I used shape of a triangle to represent the data of a single observation. Which means, now the information of a observation became more straight forward. If I want to add more information, I can also add color to the triangles to represent categorical data.

##Problem 3
#a.The t-test and Mann-Whitney test help the authors compare fish density, biomass, or size
between protected and unprotected areas. And they are trying to figure out whether hydroacustics can reliably measure the differences compared to traditional visual survey.

insert pic



































